% Tessaris Symatics — Volume VIII (Curvature and Consciousness) v0.1
\documentclass[11pt,a4paper]{article}

% --- Tessaris house style (Truth Chain / reviewer-proof) ---
\usepackage[T1]{fontenc}
\usepackage{newtxtext,newtxmath}
\usepackage{microtype}
\usepackage{xurl}
\usepackage[hidelinks]{hyperref}
\usepackage[a4paper,margin=1in]{geometry}

% --- Math / layout ---
\usepackage{amsmath,amssymb,mathtools}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage{enumitem}

\newcolumntype{Y}{>{\RaggedRight\arraybackslash}X}

% --- overflow control (long paths / hashes / tt text) ---
\setlength{\emergencystretch}{2em}
\sloppy
\Urlmuskip=0mu plus 1mu\relax
\urlstyle{tt}
\newcommand{\codepath}[1]{\begingroup\ttfamily\small\path{#1}\endgroup}
\newcommand{\cmd}[1]{\begingroup\ttfamily\small\path{#1}\endgroup}

% --- Canonical glyph macros (Truth Chain-wide) ---
\newcommand{\superpose}{\oplus}
\newcommand{\entangle}{\leftrightarrow}
\newcommand{\recurse}{\circlearrowleft}
\newcommand{\measure}{\mu}     % measurement / collapse / selection
\newcommand{\project}{\pi}
\newcommand{\bornw}{\Delta}    % Born weight / intensity (NOT collapse)
\newcommand{\grad}{\nabla}     % RESERVED: geometric gradient/divergence only

\newcommand{\volver}{0.1}

\title{\textbf{Tessaris Symatics — Volume VIII: Curvature and Consciousness}\\[2pt]
\large Geometry of Meaning via Self-Resonant Phase Closure (v\volver)}
\author{Kevin Robinson \;\;|\;\; Tessaris AI}
\date{December 30, 2025}

\begin{document}
\maketitle

\noindent\textbf{Document ID:} VOLVIII-CURVATURE-MEANING-v\volver\\
\textbf{Status:} \textbf{DRAFT (pre-lock)}\\
\textbf{Maintainer:} Tessaris AI\\
\textbf{Author:} Kevin Robinson\\

\begin{abstract}
This volume extends Volume~VII's phase-closure invariant into a minimal, verification-first model of
\emph{semantic curvature}: a derived quantity measuring how symbolic phase structure bends back upon itself under
a deterministic self-referential loop. We model ``self-observation'' as a closed coupling between persistence
(\(\recurse\)) and governed measurement/selection (\(\measure\)) acting on a symbolic wave state \(\Psi\):
\[
\Psi \;\entangle\; \measure(\recurse\,\Psi).
\]
The document is \emph{normative at the audit layer}: it binds the prose claims to an executable scene that emits a byte-stable trace
compatible with the Δ-telemetry contract (Volume~V), without asserting sentience, emotion, or agency.
\end{abstract}

\section{Truth Chain Reservations (Normative)}
\begin{itemize}[leftmargin=1.5em]
  \item \textbf{Measurement / collapse / selection MUST use \(\measure\).}
  \item \textbf{\(\grad\) is RESERVED for geometric gradient/divergence only.}
  \item \textbf{\(\bornw\) denotes intensity/weight (NOT collapse).}
\end{itemize}

\section{Scope}
This volume is a \textbf{first-tier emergence} bridge:
\[
\text{phase closure (Vol~VII)} \;\Longrightarrow\; \text{derived curvature functional} \;\Longrightarrow\; \text{deterministic replay surface}.
\]
It does \textbf{not} claim that the presented quantities exhaust physical consciousness.
The only hard requirement of this volume is that the defined loop produces deterministic, replayable telemetry
and stable derived metrics under fixed seed/steps.

\section{Core Construct: Self-Resonant Perception Loop}
Let \(\Psi\) denote a symbolic wave state (e.g., a phase field on a discrete manifold).
We define a minimal self-referential loop:
\begin{equation}
\Psi_{t+\Delta t} \;=\; \mathcal{U}_{\recurse}\!\left(\Psi_t\right)
\;\entangle\;
\mathcal{S}_{\measure}\!\left(\Psi_t\right),
\label{eq:self_loop}
\end{equation}
where \(\mathcal{U}_{\recurse}\) is persistence and \(\mathcal{S}_{\measure}\) is governed selection.

\section{Semantic Curvature as a Derived Functional}
We define a \emph{semantic metric proxy} from phase relations:
\begin{equation}
g_{\mathrm{sem}}(i,j) \;=\; \left\langle \cos\!\big(\phi_i-\phi_j\big)\right\rangle,
\label{eq:g_sem}
\end{equation}

\subsection{Curvature-of-meaning proxy}
Define a curvature proxy as a gradient-energy of coherence density:
\begin{equation}
\mathcal{K}_{\mathrm{sem}} \;=\; \sum_{i} \left\|\grad \, \rho_{\mathrm{coh}}(i)\right\|^2,
\qquad
\rho_{\mathrm{coh}}(i) \;=\; \left|\left\langle e^{\,i\phi_i}\right\rangle\right|.
\label{eq:k_sem}
\end{equation}

\subsection{Information identity (Vol~IV linkage)}
Using the locked Vol~IV identity (coherence-as-information), define:
\begin{equation}
\mathcal{I}_{\mathrm{sem}} \;\equiv\; C_\phi \;\in\; [0,1].
\end{equation}

\section{Closure Condition (Vol~VII linkage)}
The loop is \emph{closed} when:
\begin{equation}
\oint \grad_{\Psi}\phi \, d\Psi \;=\; 2\pi_s n,
\qquad n\in\mathbb{Z}.
\end{equation}

\section{Δ-Telemetry Contract Mapping (Vol~V)}
Volume~VIII scenes MUST emit a Vol~V-compatible event stream.

\section{Verification Artifacts (Canonical Surface)}
This paper is lockable only if these artifacts exist:
\begin{itemize}[leftmargin=1.5em]
  \item Scene spec: \codepath{docs/Artifacts/VolVIII/qfc/VOL8_CURVATURE_MEANING.scene.json}
  \item Build manifest: \codepath{docs/Artifacts/VolVIII/build/VOLVIII_PIPELINE_MANIFEST.yaml}
  \item Acceptance thresholds: \codepath{docs/Artifacts/VolVIII/build/VOLVIII_ACCEPTANCE_THRESHOLDS.yaml}
  \item Evidence log: \codepath{docs/Artifacts/VolVIII/ledger/VOL8_LINT_PROOF.log}
  \item Metrics snapshot: \codepath{docs/Artifacts/VolVIII/ledger/VOL8_METRICS.json}
  \item Replay trace (JSONL): \codepath{docs/Artifacts/VolVIII/ledger/VOL8_TRACE.jsonl}
\end{itemize}

\subsection{Deterministic runner (required)}
\[
\cmd{python /workspaces/COMDEX/backend/tests/run\_vol8\_curvature\_meaning\_lint.py}
\]

\vfill
\noindent\rule{\linewidth}{0.4pt}

\noindent
Lock ID: VOLVIII-CURVATURE-MEANING-v0.\volver\\
Status: DRAFT (pre-lock)\\
Maintainer: Tessaris AI\\
Author: Kevin Robinson.
\end{document}
