% TRUCHAIN_PAEV_ATOMS_V0.tex
% TruChain / PAEV Atom Ladder (Audit-grade)
\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{newtxtext,newtxmath}
\usepackage{microtype}
\usepackage{xurl}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{margin=1in}

\setlist[itemize]{leftmargin=*, itemsep=0.25em, topsep=0.25em}
\setlist[enumerate]{leftmargin=*, itemsep=0.25em, topsep=0.25em}

\newcolumntype{Y}{>{\RaggedRight\arraybackslash}X}

\title{TruChain PAEV Atom Ladder v0 (Audit Notebook)}
\author{Kevin Robinson (Tessaris AI)}
\date{\today}

\begin{document}
\maketitle

\section{Purpose}
This document is the audit notebook for the \textbf{PAEV Atom Ladder}: a staged, falsifiable test program that moves from
\textbf{simulation invariants} to \textbf{physical wave-field demonstrations} and then to \textbf{atom-adjacent proxies}
(without overclaiming).

\textbf{Primary goal:} demonstrate that the PAEV ``wave program'' grammar yields reproducible, measurable control effects,
and that those effects survive transition from simulation to hardware proxies.

\textbf{Guardrails (MUST):}
\begin{itemize}
  \item The ladder MUST avoid biological / wetlab claims.
  \item The ladder MUST avoid claims of atomic manipulation unless measurements explicitly support them.
  \item Each non-simulation rung MUST be backed by immutable artifacts (raw logs + SHA256) and a measured results JSON.
\end{itemize}

\section{Repository anchors (what to read)}
\begin{itemize}
  \item Simulation tests: \url{Glyph_Net_Browser/src/sim/tests/}
  \item PAEV ladder tests: \url{backend/paev_ladder/tests/}
  \item Measured results JSON: \url{backend/paev_ladder/results/}
  \item Raw artifact drops + SHA256SUMS: \url{backend/paev_ladder/raw/}
\end{itemize}

\section{Ladder overview}
The ladder is organized as rungs with explicit \textbf{pass criteria} and \textbf{evidence requirements}.
Simulation rungs assert invariants in code. Physical/proxy rungs assert thresholds against measured results JSON
that MUST correspond to raw artifacts.

\subsection*{A --- Simulation (prove grammar + invariants)}
\begin{itemize}
  \item \textbf{A1 Topology Gate Causality (Freeze + g sweep)}\\
    Claim: \texttt{topo\_gate01} is a real control input; Freeze pins topology deterministically.\\
    Pass: Freeze cuts topology-change-rate $\ge 90\%$ AND at least one stability metric monotonic with $g$ ($\rho \ge 0.7$).

  \item \textbf{A2 Resonant Addressing (Node Frequency IDs)}\\
    Claim: nodes are selectively addressable by wave tokens $(\omega,\phi,A)$, not global gain.\\
    Pass: selectivity $S \ge 5$ and crosstalk $X \le 0.2$ for $\ge 80\%$ targets across seeds.

  \item \textbf{A3.1 Chiral Handshake (Protocol Compatibility Gate)}\\
    Claim: chirality acts as a header that gates coupling (match $\rightarrow$ couple, mismatch $\rightarrow$ suppress).\\
    Pass: $\Delta\text{coupling} = C_{\text{match}} - C_{\text{mismatch}} > 3\sigma$ across trials; decode-error jumps on mismatch.

  \item \textbf{A4 Wormhole / k\_link vs Distance (Adjacency beats geometry)}\\
    Claim: informational adjacency changes coordination independent of Euclidean distance (in-sim).\\
    Pass: distance sensitivity (slope) drops $\ge 50\%$ with \texttt{k\_link} enabled (equal energy budget).
\end{itemize}

\subsection*{B --- Physical wave-field (prove ``wave program writes geometry'')}
\begin{itemize}
  \item \textbf{B1 Chladni Pattern Compiler (geometry-from-program)}\\
    Pass: similarity $\ge 0.8$ on $\ge 3$ distinct target modes; robustness drop $\le 0.1$ under small perturbations.

  \item \textbf{B2 Trap Node Control (deterministic routing)}\\
    Pass: RMSE $< 5\%$ travel range; dropout $< 10\%$ at moderate speed.

  \item \textbf{B3 Information Channel (symbols over waves)}\\
    Pass: SER $< 5\%$ at nominal SNR with graceful degradation curve.
\end{itemize}

\subsection*{C --- Atom-adjacent proxy (cash-out toward relevance without overclaiming)}
\begin{itemize}
  \item \textbf{C1 EM Resonant Addressing Proxy (LC ``atoms'' + routing)}\\
    Pass: selectivity $\ge 5$; topology-rule success $\ge 90\%$; stable under detuning sweep.

  \item \textbf{C2 Two-level-system emulator (optional but strong)}\\
    Pass: fidelity above baseline and fidelity $\ge 0.80$.

  \item \textbf{C4 Multi-node Structural Hold (``acoustic molecule'')}\\
    Pass: stable hold for $T$ seconds with bounded shape error; recovery $\ge 80\%$; beats independent-traps baseline.
\end{itemize}

\section{What is locked in so far (as of this repo state)}
\subsection{Simulation rungs (A)}
\begin{itemize}
  \item A2: \textbf{PASS} (Vitest)
  \item A3.1: \textbf{PASS} (Vitest)
  \item A4: \textbf{PASS} (Vitest)
  \item A1: \textbf{SKIPPED} (present but not enforced)
\end{itemize}

\subsection{Physical / proxy rungs (B/C)}
These rungs are enforced by \texttt{pytest} reading \texttt{backend/paev\_ladder/results/<RUNG>.json}.
In non-strict mode, missing measurement results SKIP; in strict mode (\texttt{PAEV\_STRICT=1}), missing measurement results FAIL.

\begin{itemize}
  \item B2: \textbf{MEASURED} result exists; \textbf{PASS} in strict mode.
  \item B3: \textbf{MEASURED} result exists; \textbf{PASS} in strict mode.
  \item B1, C1, C2, C4: \textbf{MISSING\_MEASUREMENT} (currently FAIL in strict mode).
\end{itemize}

\section{Artifacts we MUST preserve (before we forget)}
\subsection{Simulation artifacts (A)}
\begin{itemize}
  \item Test definitions and thresholds:
    \begin{itemize}
      \item \url{Glyph_Net_Browser/src/sim/tests/A1_topology_gate_causality.test.ts}
      \item \url{Glyph_Net_Browser/src/sim/tests/A2_resonant_addressing.test.ts}
      \item \url{Glyph_Net_Browser/src/sim/tests/A31_chiral_handshake.test.ts}
      \item \url{Glyph_Net_Browser/src/sim/tests/A4_klink_vs_distance.test.ts}
    \end{itemize}
\end{itemize}

\subsection{Measurement artifacts (B/C)}
For each physical/proxy rung $R$:
\begin{itemize}
  \item Raw artifacts MUST be dropped under \url{backend/paev_ladder/raw/\$R/}
  \item A \texttt{SHA256SUMS.txt} MUST be generated over raw files (immutable evidence anchor)
  \item A measured summary JSON MUST exist under \url{backend/paev_ladder/results/\$R\_*.json} matching the rung loader name
\end{itemize}

\subsection{Result JSON minimal contract (current)}
Result JSON files MUST include \texttt{status} and all keys asserted by the rung test. Recommended additions
(for audit-grade traceability) SHOULD include:
\begin{itemize}
  \item \texttt{run\_id}, \texttt{ran\_at\_utc}, \texttt{operator}
  \item \texttt{device\_id} / \texttt{rig\_version}, \texttt{firmware\_version}
  \item \texttt{raw\_artifact\_dir}: path to raw folder
  \item \texttt{raw\_sha256sums}: sha256 of \texttt{SHA256SUMS.txt} (or embed its contents)
  \item \texttt{notes}: free text
\end{itemize}

\section{Current pass/fail dashboard}
\begin{tabularx}{\linewidth}{l l Y}
\textbf{Rung} & \textbf{Status} & \textbf{Evidence / Location} \\
\hline
A1 & SKIPPED & \url{Glyph_Net_Browser/src/sim/tests/A1_topology_gate_causality.test.ts} \\
A2 & PASS & \url{Glyph_Net_Browser/src/sim/tests/A2_resonant_addressing.test.ts} \\
A3.1 & PASS & \url{Glyph_Net_Browser/src/sim/tests/A31_chiral_handshake.test.ts} \\
A4 & PASS & \url{Glyph_Net_Browser/src/sim/tests/A4_klink_vs_distance.test.ts} \\
B1 & MISSING\_MEASUREMENT & \url{backend/paev_ladder/results/B1_chladni_pattern_compiler.json} \\
B2 & PASS (MEASURED) & \url{backend/paev_ladder/results/B2_trap_node_control.json} \\
B3 & PASS (MEASURED) & \url{backend/paev_ladder/results/B3_information_channel.json} \\
C1 & MISSING\_MEASUREMENT & \url{backend/paev_ladder/results/C1_em_resonant_addressing_proxy.json} \\
C2 & MISSING\_MEASUREMENT & \url{backend/paev_ladder/results/C2_two_level_emulator.json} \\
C4 & MISSING\_MEASUREMENT & \url{backend/paev_ladder/results/C4_multinode_structural_hold.json} \\
\end{tabularx}

\section{What remains to ``finish these off''}
\begin{enumerate}
  \item Decide whether to un-skip A1 (turn it into an enforced invariant) or keep as future rung.
  \item Produce real measurement artifacts for B1/C1/C2/C4:
    \begin{itemize}
      \item Drop raw logs/files into \url{backend/paev_ladder/raw/<RUNG>/}
      \item Generate \texttt{SHA256SUMS.txt}
      \item Produce a \texttt{status=MEASURED} results JSON satisfying the test keys and thresholds
      \item Run \texttt{PAEV\_STRICT=1 pytest -q backend/paev\_ladder/tests} until green
    \end{itemize}
\end{enumerate}

\section{Lock footer}
\begin{flushleft}
\textbf{Lock ID:} TRUCHAIN-PAEV-ATOMS-V0\\
\textbf{Status:} DRAFT\_LOCK\_PENDING\_MEASUREMENTS\\
\textbf{Maintainer:} Tessaris AI\\
\textbf{Author:} Kevin Robinson.
\end{flushleft}

\end{document}
