% Volume IV — Information Theory: Coherence as Information (v0.1)
\documentclass[11pt,a4paper]{article}

% --- Tessaris house style ---
\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{newtxtext,newtxmath}
\usepackage{microtype}
\usepackage{xurl}
\usepackage[hidelinks]{hyperref}

\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage{enumitem}

\newcolumntype{Y}{>{\RaggedRight\arraybackslash}X}

% --- Truth Chain macros (normative) ---
\newcommand{\superpose}{\oplus}
\newcommand{\entangle}{\leftrightarrow}
\newcommand{\recurse}{\circlearrowleft}
\newcommand{\measure}{\mu}     % measurement / collapse / selection
\newcommand{\project}{\pi}
\newcommand{\bornw}{\Delta}    % Born weight / intensity (NOT collapse)
\newcommand{\grad}{\nabla}     % RESERVED: geometric gradient/divergence only

\title{\textbf{Volume IV — Information Theory: Coherence as Information}\\[2pt]
\large Codex / Symatics Algebra Series (v0.1)}
\author{Kevin Robinson \;\;|\;\; Tessaris AI}
\date{October 11, 2025}

\begin{document}
\maketitle

\begin{abstract}
Classical information theory defines information as reduction of uncertainty over discrete symbols.
In Symatics, symbols are continuously coupled through superposition ($\superpose$) and entanglement ($\entangle$).
This paper defines information as \emph{phase coherence} and entropy as \emph{phase decoherence} (loss of resonance),
providing the metric bridge required for governed selection and later energetic unification.
\end{abstract}

\section{Definitions in Force (Truth Chain)}
\begin{itemize}[noitemsep]
\item \textbf{Collapse/selection:} MUST use $\measure$ (not $\grad$).
\item \textbf{Gradient:} $\grad$ is RESERVED for geometry/physics only.
\item \textbf{Born weight:} MUST use $\bornw$ for intensity/selection weight; it is not collapse.
\end{itemize}

\section{Core discovery}
\begin{itemize}[noitemsep]
\item \textbf{Information} is \textit{coherence}: phase-aligned symbolic waves remain structurally intact.
\item \textbf{Entropy} is \textit{loss of resonance}: phase dispersion increases and coherence decays.
\item \textbf{Communication} is \textit{resonance maintenance}: alignment across entangled channels.
\end{itemize}

\[
\boxed{\text{Information = Coherence \quad Entropy = Phase Dispersion}}
\]

\section{From bits to wave-ensembles}
Shannon assumes independent symbols and uncertainty.
Symatics replaces independence with coupled wave ensembles:
\[
S_i = \superpose_j \psi_j(x,t),
\]
with cross-channel constraints propagated by $\entangle$.
A message is a resonance ensemble, not isolated bits.

\section{Coherence metric and information identity}
Let $\Delta\phi$ be the phase difference between components in an ensemble (or between two coupled systems).
Define phase coherence
\[
C_\phi := \left|\left\langle e^{i\Delta\phi}\right\rangle\right|\in[0,1],
\qquad
D_\phi := 1 - C_\phi.
\]
\textbf{Information is coherence}:
\[
\mathcal{I} := 1 - D_\phi = C_\phi.
\]
Define symbolic entropy relative to a baseline coherence $C_{\phi,0}>0$:
\[
\mathcal{S}_{\mathrm{sym}} := -\ln\!\left(\frac{C_\phi}{C_{\phi,0}}\right).
\]
Thus $\Delta\phi\to 0 \Rightarrow C_\phi\to 1$ and $\mathcal{S}_{\mathrm{sym}}\to 0$.

\section{Resonant information flow}
For systems $A$ and $B$,
\[
\mathcal{I}_{A\entangle B} := \left|\left\langle e^{i(\phi_A-\phi_B)}\right\rangle\right|.
\]
$\mathcal{I}_{A\entangle B}=1$ corresponds to perfect phase alignment (maximal mutual coherence).

\section{Thermodynamic analogy}
For isolated ensembles, phase dispersion is non-decreasing (decoherence):
\[
\frac{d\mathcal{S}_{\mathrm{sym}}}{dt}\ge 0.
\]
With feedback coupling (entanglement channels) the system can locally restore coherence; operationally this is the metric basis for pruning high-dispersion branches prior to governed selection.

\section{Implications for cognition and communication}
Learning strengthens coherence; forgetting is decoherence.
Information processing is coherence management: maintaining high $\mathcal{I}$ across interacting $\superpose$-states and entangled constraints.

\section{Repro hooks}
This document is verified by a QFC scene that demonstrates phase locking and reports acceptance metrics:
\begin{itemize}[noitemsep]
\item Scene: \texttt{docs/Artifacts/VolIV/qfc/VOL4\_COHERENCE\_PHASE\_LOCK.scene.json}
\item Thresholds: \texttt{docs/Artifacts/VolIV/build/VOLIV\_ACCEPTANCE\_THRESHOLDS.yaml}
\end{itemize}

\vfill
\noindent\rule{\linewidth}{0.4pt}

\noindent
Lock ID: VolIV-INFO-COHERENCE-v0.1\\
Status: PENDING (until artifacts + thresholds are satisfied)\\
Maintainer: Tessaris AI\\
Author: Kevin Robinson.

\end{document}
