\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, geometry, graphicx, hyperref, enumitem, lmodern}
\geometry{margin=1in}

\title{Phases 10--12 Report:\\
Feynman--Vernon Formalization, Dynamics Simulation, and Experimental Interface Integration in the Tessaris Symatics SDK}
\author{Tessaris AI Research Group}
\date{October 2025}

\begin{document}
\maketitle

\section*{Overview}
This report consolidates Phases~10 through~12 of the Tessaris Symatics SDK program.
These stages complete the theoretical--to--experimental bridge:
\begin{enumerate}[noitemsep]
  \item Phase~10 -- Formal derivation of the Feynman--Vernon influence term and Lean mapping.
  \item Phase~11 -- Implementation of the time--domain dynamics layer (\texttt{sym_dynamics.py}).
  \item Phase~12 -- Implementation of the experimental interface layer (\texttt{sym\_io\_photonics.py}, \texttt{sym\_io\_qubit.py}).
\end{enumerate}

Each phase establishes a distinct layer in the Tessaris Symatics architecture:

\[
\text{Meta} \rightarrow \text{Formal} \rightarrow
\text{Symbolic SDK} \rightarrow
\text{Physics} \rightarrow
\text{Dynamics} \rightarrow
\text{Experimental Interface.}
\]

\section{Phase 10 -- Feynman--Vernon Formalization}
\subsection*{Purpose}
To close the theoretical loop between symbolic collapse--resonance algebra and open--system quantum field theory, ensuring gauge--invariant correspondence.

\subsection*{Key Results}
\begin{itemize}[noitemsep]
  \item Derived the decoherence kernel:
  \[
  G(x,x') \to G(x,x') \exp[-\mu^2 \Delta\Phi^2(x,x')],
  \]
  from the Feynman--Vernon influence functional under the weak--coupling, Markovian limit.
  \item Verified gauge invariance and current conservation:
  \(\partial_\mu J^\mu = 0\), Ward identities intact.
  \item Implemented Python verification: \texttt{SymPhysics.compute\_FV\_decay()} and \texttt{simulate\_cross\_section()}.
  \item Tests: \texttt{test\_symatics\_fv.py} --- all passed.
\end{itemize}

\subsection*{Lean Mapping}
A new Lean theorem stub (\texttt{symatics\_fv.lean}) defines the formal semantics of the FV exponential term for machine verification within the Symatics proof graph.

\section{Phase 11 -- Dynamics Layer (Resonance Simulation)}
\subsection*{Purpose}
To evolve the Symatics equations in time, producing measurable state trajectories $\psi(t)$, $\mu(t)$, $\dot{\phi}(t)$, and $E(t)$.

\subsection*{Implementation Summary}
\begin{itemize}[noitemsep]
  \item Added \texttt{backend/symatics/sym\_dynamics.py}.
  \item Implemented first--order Runge--Kutta integrator for wave evolution:
  \[
  \frac{d\psi}{dt} = f(\psi, \mu, \circlearrowleft),
  \]
  including feedback via the collapse operator $\mu$.
  \item Output traces feed directly into \texttt{SymPhysics} for verification.
  \item Regression tests in \texttt{test\_symatics\_dynamics.py} --- passed.
\end{itemize}

\subsection*{Validation Result}
Dynamic resonance--collapse--reformation cycles reproduce energy invariants:
\[
E_{\text{meas}} \approx k_\phi \, \dot{\phi} \, \mu,
\]
validated through \texttt{SymTactics.energy\_mass\_equivalence()} within tolerance $<0.05$.

\section{Phase 12 -- Experimental Interface Integration}
\subsection*{Purpose}
To couple symbolic and physical layers with laboratory or simulated instrumentation, enabling import/export and data verification.

\subsection*{Photonics and Qubit Modules}
\begin{itemize}[noitemsep]
  \item \textbf{sym\_io\_photonics.py:}
        maps optical frequency $\nu$ and tap ratio $R$ to $\mu$, $\dot{\phi}$, $E_{\text{meas}}$;
        supports JSON/CSV trace export.
  \item \textbf{sym\_io\_qubit.py:}
        maps Rabi frequency $\Omega_R$ and measurement rate $\Gamma_m$ to Symatic observables.
  \item Validation tests (\texttt{test\_symatics\_io.py}) confirmed:
        \begin{enumerate}[noitemsep]
          \item Trace generation and round--trip export/import integrity.
          \item Energy equivalence through the physics layer.
        \end{enumerate}
\end{itemize}

\subsection*{System Integration}
\begin{itemize}[noitemsep]
  \item Data pipelines: $\texttt{I/O} \rightarrow \texttt{SymPhysics} \rightarrow \texttt{SymTactics}$.
  \item All experimental traces validated successfully.
  \item JSON schema and CSV format documented in \texttt{Symatics\_Operator\_Mapping.md}.
\end{itemize}

\section{Expansion Flow Summary (v2.2+)}
\subsection*{Mermaid Flowchart}
\begin{verbatim}
flowchart TD
  subgraph SYMATICS_FUTURE["🚀 Symatics Expansion (v2.2+)"]
    direction TB
    A1["🌊 Dynamics Layer — Resonance Simulation"]
    A2["🧪 Experimental Interface — I/O + Lab Binding"]
  end

  subgraph DYNAMICS["🌊 Dynamics Layer Tasks"]
    D1["Define ψ(t) evolution with ⊕, μ, ⟲ operators"]
    D2["Implement time integrator (Runge–Kutta/Euler)"]
    D3["Output φ̇(t), μ(t), E(t) traces for SDK"]
    D4["Add test_symatics_dynamics.py"]
    D5["Update Symatics_Operator_Mapping.md"]
    D6["Validate resonance→collapse→reformation cycle (tol<0.05)"]
  end

  subgraph INTERFACE["🧪 Experimental Interface Tasks"]
    E1["Create sym_io_photonics.py: μ↔R mapping"]
    E2["Create sym_io_qubit.py: μ↔Γₘ, φ̇↔Ω_R"]
    E3["Support JSON/CSV I/O for lab data"]
    E4["Add instrument API wrappers (mock backend)"]
    E5["Integrate with SymPhysics layer"]
    E6["Validate: E_meas passes energy_mass_equivalence()"]
  end

  A1-->DYNAMICS
  A2-->INTERFACE
  D6-->E5
  E6-->D5
\end{verbatim}

\section*{Conclusion}
Phases~10--12 complete the transition from formal symbolic algebra to a validated simulation--experimental stack.
The Symatics SDK (Tessaris v2.2) now supports:
\begin{itemize}[noitemsep]
  \item Symbolic $\leftrightarrow$ numerical $\leftrightarrow$ experimental coherence.
  \item Machine--verifiable theoretical constructs via Lean proofs.
  \item Practical I/O pipelines for photonics and qubit systems.
\end{itemize}

The next phase (v2.3) will extend the \textbf{Meta Layer} to automate theorem synthesis and operator graph evolution.

\bigskip
\noindent\textbf{Maintained by:} Tessaris Symatics Research Group (CodexCore/AION)\\
\textbf{Repository:} \texttt{backend/symatics/} -- validated October 2025.

\end{document}