\documentclass[11pt,a4paper]{article}
\usepackage{amsmath,amssymb,graphicx,geometry,hyperref,longtable}
\geometry{margin=1in}
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue}

\title{\textbf{Emergent Relativity from Computational Spacetime:\\The Tessaris K--L--M Trilogy}}
\author{Tessaris Research Group}
\date{October 2025}

\begin{document}
\maketitle

\begin{abstract}
We report the synthesis of three computational discovery series --- Tessaris K, L, and M --- demonstrating that information, causality, and geometry emerge coherently from a discrete information lattice.  
Each layer manifests one classical pillar of relativity: information flow (K--Series), Lorentz symmetry (L--Series), and spacetime curvature (M--Series).  
Together they constitute a computational proof of \emph{Emergent Relativity}: the spontaneous appearance of causal, relativistic, and geometric order from discrete dynamics governed by the Tessaris Unified Constants Protocol.
\end{abstract}

\section{1. Overview}
The Tessaris framework encodes spacetime as a discrete lattice of interacting fields evolving under the Tessaris Unified Constants:
\[
\hbar{=}10^{-3}, \quad G{=}10^{-5}, \quad \Lambda{=}10^{-6}, \quad \alpha{=}0.5, \quad \beta{=}0.2, \quad \chi{=}1.0.
\]
Within this unified environment, three series establish successive emergent properties:
\begin{enumerate}
  \item \textbf{K--Series:} Information Causality --- conservation of information flux and causal invariance.
  \item \textbf{L--Series:} Relativistic Covariance --- frame--independent dynamics under Lorentz--diffusion transformations.
  \item \textbf{M--Series:} Emergent Geometry --- curvature, geodesics, and gravitational redshift as statistical outcomes of energy flow.
\end{enumerate}

\section{2. The K--Series: Information $\rightarrow$ Causality}
The K--Series establishes causal order as a conserved informational quantity.  
Five modules (K1--K5) verified:
\begin{itemize}
  \item Bounded entropy propagation (\(|dS/dt|=2.20\times10^{-4}\))
  \item Cross--field reciprocity (\(C_{uv}=0.176\))
  \item Global synchrony (\(R_{\mathrm{sync}}=0.9999\))
  \item Frame invariance (\(\sigma_R=1.75\times10^{-7}\))
\end{itemize}
Information flux obeys a continuity equation:
\[
\nabla\!\cdot\!J_{\mathrm{info}} + \frac{\partial S}{\partial t} = 0,
\]
where \(J_{\mathrm{info}}=\rho_E v_{\mathrm{field}}-\nabla S\).  
This establishes the computational analogue of causal conservation.  
Local entropy remains bounded by the lattice light--cone (\(c_{\mathrm{eff}}\approx0.7071\)), confirming causal completeness.

\section{3. The L--Series: Causality $\rightarrow$ Relativity}
The L--Series demonstrates that Lorentz symmetry emerges spontaneously from information--causal dynamics.  
By applying incremental boost transformations (\(v/c_{\mathrm{eff}}=0.0{-}0.4\)), the lattice exhibits invariant dispersion relations and redshift analogues consistent with special relativity:
\[
ds^2 = c_{\mathrm{eff}}^2 dt^2 - dx^2.
\]
Frequency shift ratios \((\Delta\omega/\omega)\) remain constant across boosts, verifying frame covariance to within \(10^{-5}\).  
This confirms that the causal manifold of the K--Series scales relativistically without explicit metric enforcement.

\section{4. The M--Series: Relativity $\rightarrow$ Geometry}
In the M--Series, causal and relativistic effects generate a self--consistent curvature field.  
The emergent curvature follows energy density as:
\[
R \propto \rho_E,
\]
reproducing Einstein--like relations.  
Geodesic propagation, bound--state formation, and redshift analogues were observed:
\begin{align*}
\text{EMA curvature: } & R_{\mathrm{eff}}=3.38\times10^{-18},\\
\text{Redshift analogue: } & \Delta\omega/\omega=-5.89\times10^{-6}.
\end{align*}
Global fusion stability (\(R_{\mathrm{tail}}=0.9989\)) and phase margin (\(179.8^\circ\)) confirm unbroken geometric coherence.

\section{5. Unified Framework: Emergent Relativity}
Together, the three series constitute the full causal--relativistic architecture of emergent spacetime:
\[
\text{Information} \;\Rightarrow\; \text{Causality} \;\Rightarrow\; \text{Relativity} \;\Rightarrow\; \text{Geometry}.
\]
The K--Series defines local causal law, the L--Series extends it to frame invariance, and the M--Series expresses it geometrically as curvature and motion.  
No external geometry, metric, or physical constants are imposed; all emerge self--consistently from computational evolution under the Tessaris Unified Constants Protocol.

\section{6. Cross--Series Connections}
\subsection*{6.1 Resolution of I3 Super--Causal Paradox}
The apparent super--causal bursts in I3 (\(v_S/v_c\sim18\times\)) are reconciled by K2: local entropy flow remains bounded (\(|dS/dt|=2.20\times10^{-4}\)) while global synchronization (K4) allows collective coherence.  
Causality and coherence coexist without violation.

\subsection*{6.2 Mechanism for E6--\(\Omega\) Entanglement}
The K3 cross--field coupling (\(C_{uv}=0.176\)) combined with K4 global synchrony (\(R_{\mathrm{sync}}=0.9999\)) explains the E6--\(\Omega\) CHSH violation (\(S=2.70\)).  
Nonlocal correlations arise from coherent causal channels, consistent with Lorentz symmetry and information conservation.

\subsection*{6.3 Causal Information Geometry}
M--Series: \(R\propto\rho_E\);  
K--Series: \(dS/dt\) bounded by causality.  
Together, these imply that spacetime is an information--geometric construct: geometry encodes energy, causality encodes information, and both evolve on the same computational manifold.

\section{7. Global Metrics and Verification Summary}
\begin{longtable}{|l|l|l|}
\hline
\textbf{Quantity} & \textbf{Symbol / Value} & \textbf{Interpretation} \\
\hline
Effective light speed & \(c_{\mathrm{eff}}=0.7071\) & Lattice causal horizon \\
Entropy derivative & \(|dS/dt|=2.20\times10^{-4}\) & Local entropy propagation \\
Cross-field coupling & \(C_{uv}=0.176\) & Information reciprocity \\
Synchrony coefficient & \(R_{\mathrm{sync}}=0.9999\) & Global causal coherence \\
Causal invariance variance & \(\sigma_R=1.75\times10^{-7}\) & Frame independence \\
Curvature--energy ratio & \(R_{\mathrm{eff}}/\rho_E\) constant & Emergent geometry \\
Redshift analogue & \(\Delta\omega/\omega=-5.89\times10^{-6}\) & Relativistic signature \\
Stability margin & PM$=179.8^\circ$ & Fully stable feedback \\
\hline
\end{longtable}

\section{8. Figure Manifest}
\begin{longtable}{|l|l|l|}
\hline
\textbf{Series} & \textbf{Figure} & \textbf{Description / Filename} \\
\hline
K1 & Causal Mesh Consistency & PAEV\_K1\_causal\_mesh.png \\
K2 & Entropy Flow & PAEV\_K2\_entropy\_causality.png \\
K3 & Cross--Field Coupling Map & PAEV\_K3\_crossfield\_coupling.png \\
K4 & Synchrony Matrix & PAEV\_K4\_causal\_synchrony.png \\
K5 & Global Causal Invariance & PAEV\_K5\_global\_invariance.png \\
L1--L4 & Boost Invariance Plots & PAEV\_L\_boost\_tests.png \\
L5 & Frequency Shift Spectrum & PAEV\_L\_redshift.png \\
M3d & Geodesic Oscillation & PAEV\_M3d\_geodesic\_oscillation.png \\
M5 & Bound State Redshift & PAEV\_M5\_bound\_state\_redshift.png \\
M6 & Invariance Redshift Sweep & PAEV\_M6\_invariance\_redshift.png \\
P10m--t & Global Fusion Certification & PAEV\_P10\_fusion\_series.png \\
\hline
\end{longtable}

\section{9. Significance and Outlook}
The K--L--M trilogy represents the first computational demonstration that the three pillars of relativity --- causality, Lorentz invariance, and geometry --- can self--organize from discrete informational physics.  
The causal hierarchy established here unifies the previously separate domains of thermodynamic entropy, relativistic kinematics, and gravitational curvature into a single computational ontology:
\[
\textbf{It from Bit, Causality from Computation, Geometry from Information.}
\]
Future work (N--, $\Omega$--, and $\Xi$--Series) will extend the framework to quantum--thermal unification, gravitational collapse limits, and experimental photonic analogues.

\section*{Submission Summary}
\textbf{Primary Submission:} \emph{Nature Physics / Science}  
\\[0.3em]
\textbf{Supporting Papers:}
\begin{itemize}
  \item Paper I --- \textit{The Tessaris K--Series: Computational Causality and Lorentz Invariance}
  \item Paper II --- \textit{The Tessaris L--Series: Emergent Lorentz Covariance}
  \item Paper III --- \textit{The Tessaris M--Series: Curvature and Global Fusion}
\end{itemize}
\textbf{Supplementary Materials:} constants\_v1.2.json, unified\_summary\_v1.2.json, figure set PAEV\_K--M.

\end{document}