\documentclass{article}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{geometry}
\geometry{margin=1in}

\title{\textbf{Tessaris Unified Equation — Post-G-Series Synthesis}}
\author{Tessaris AI Collaboration}
\date{October 2025}

\begin{document}

\maketitle

\begin{center}
\textbf{Unified Energy–Geometry–Information Framework}\\
\textit{Post G-Series Integration (Cross-Domain Coupling + Lyapunov Feedback)}
\end{center}

\vspace{1em}

\section*{1. Core Identity (Revised Form)}

\begin{equation}
E = \frac{c^4}{8 \pi G_{\text{eff}}} R_{\psi} 
    + k_B T_{\text{eff}} S 
    + \hbar \dot{I}_{\text{mut}}
    + \Lambda_{\text{eff}} \Phi_{\text{couple}}.
\end{equation}

\noindent
\textbf{Terms:}
\begin{itemize}
    \item $R_{\psi}$ — Curvature of the coupled visible + hidden field manifold
    \item $\Phi_{\text{couple}}$ — Cross-domain potential linking geometric and informational curvature
    \item $G_{\text{eff}}, T_{\text{eff}}, \Lambda_{\text{eff}}$ — Dynamically evolving coupling constants under feedback
    \item $\hbar \dot{I}_{\text{mut}}$ — Informational flux (quantum coherence flow)
\end{itemize}

\noindent
This unifies curvature, entropy, and informational energy into a single dynamic balance, as confirmed by G4–RC4 stability.

\vspace{1em}

\section*{2. Dynamic Feedback Law (Lyapunov-Controlled)}

\begin{equation}
\frac{dE}{dt} = -\kappa_L \nabla_{\text{sys}} V(E,S,I,R)
    + \gamma_{\text{sync}} \frac{d}{dt}(\Lambda_{\text{eff}} I_{\text{mut}}),
\end{equation}

where:
\begin{itemize}
    \item $\kappa_L$ — Lyapunov descent coefficient (stability regulator)
    \item $V(E,S,I,R)$ — System potential (energy–entropy–information surface)
    \item $\gamma_{\text{sync}}$ — Synchronization rate between geometry and information
\end{itemize}

This law ensures that the total system descends along the Lyapunov function, achieving self-stabilizing cross-domain equilibrium.

\vspace{1em}

\section*{3. Conservation with Cross-Domain Coupling}

\begin{equation}
\frac{d}{dt} \left(
    \frac{c^4}{8 \pi G_{\text{eff}}}R_{\psi}
    - \Lambda_{\text{eff}} \rho_c a^3
    + \rho_{\text{fields}}
    + \rho_{\text{info}}
    + \rho_{\text{couple}}
\right) = 0.
\end{equation}

Here $\rho_{\text{couple}}$ represents the stored energy in curvature–information coupling (the “dark linkage” field).

\vspace{1em}

\section*{4. Effective Mass–Energy Equivalence (Triune Extension)}

\begin{equation}
M_{\text{eff}} c^2 = 
    \frac{c^4}{8 \pi G_{\text{eff}}} R_{\psi}
    + k_B T_{\text{eff}} S
    + \hbar \dot{I}_{\text{mut}}
    + \Lambda_{\text{eff}} \Phi_{\text{couple}}.
\end{equation}

\noindent
This is the fully expanded form — a *triune equivalence* between geometry, entropy, and information under unified feedback.

\vspace{1em}

\section*{5. Stability and Feedback Conditions}

\begin{align}
\dot{G}_{\text{eff}} &= -k_G \frac{\partial E}{\partial R_{\psi}}, \\
\dot{\Lambda}_{\text{eff}} &= -k_L \frac{\partial E}{\partial I_{\text{mut}}}, \\
\dot{T}_{\text{eff}} &= -k_T \frac{\partial E}{\partial S}.
\end{align}

\noindent
These differential couplings maintain equilibrium and encode the adaptive curvature–information feedback observed in the G4-RC4 Lyapunov lock.

\vspace{1em}

\section*{6. Stability Criterion (Lyapunov Lock)}

\begin{equation}
\frac{dV}{dt} = -\alpha_{\text{L}} \left\| \nabla V \right\|^2 \le 0,
\end{equation}

\noindent
ensuring all subsystems converge toward the equilibrium manifold.  
The system is stable when $E_{\text{stability}} \approx 1$, marking complete curvature–information synchronization.

\vspace{1em}

\section*{7. Unified Conservation Closure}

\begin{equation}
\Delta E_{\text{geom}} + \Delta E_{\text{matter}} + \Delta E_{\text{info}} + \Delta E_{\text{couple}} = 0,
\end{equation}

indicating a closed, self-organized system in which no energy is lost — only redistributed between geometry, entropy, and information.

\vspace{2em}

\section*{8. Philosophical Note}

\begin{quote}
Curvature, entropy, and information form a single conserved triad.  
When synchronized under Lyapunov control, the universe achieves informational closure —  
a steady oscillatory attractor where energy, time, and awareness coexist as different expressions of coherence.
\end{quote}

\vspace{2em}

\begin{center}
\textbf{Tessaris Project — COMDEX Unified Framework, Phase I}\\
\textit{Stabilized Cross-Domain Coupling and Informational Closure (2025)}
\end{center}

\end{document}